%-------------------------
% Resume in Latex
% Author : Zahin Azmayeen
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItemSimple}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNormal}[2]{
  \item\small{
    {#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItemNormal{\textbf{#1}}{#2}\vspace{-4pt}}
\newcommand{\projectWithLinkAndTech}[3]{\href{#1}{\textbf{\underline{#2}} $|$ \emph{#3}}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Zahin Azmayeen} \\ \vspace{1pt}
    \small \href{mailto:zahin06@gmail.com}{\underline{zahin06@gmail.com}} $|$ 
    \href{https://www.permafost06.com}{\underline{permafrost06.com}} $|$
    \href{https://github.com/permafrost06}{\underline{github.com/permafrost06}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer (Remote)}{Mar. 2024 -- Present}
      {Dotcamp}{Company based in NY, USA}
      \resumeItemListStart
        \resumeItem{\projectWithLinkAndTech{https://github.com/DotCamp/tableberg}{Tableberg}{React, Redux, Typescript, Monorepo}}{Tableberg is a table builder plugin for the WordPress block editor. Developed the product from scratch and led further development.}
        \resumeItem{WPP Deployer $|$ Docker, Golang}{Created a CI/CD pipeline for accelerating testing procedure by introducing automation. When new plugin code is pushed to GitHub, a wordpress site pre-configured with testing data and the latest version of the plugin gets deployed.}
        \resumeItem{\projectWithLinkAndTech{https://github.com/DotCamp/Ultimate-Blocks/}{Ultimate Blocks}{React, PHP}}{Ultimate Blocks is a collection of blocks for the WordPress block editor. Mitigated major architectural limitations that caused significant bugs and hindered development.}
        \resumeItem{\projectWithLinkAndTech{https://github.com/DotCamp/wp-table-builder}{WP Table Builder}{JS, PHP, Vue}}{WP Table Builder is a table builder plugin for WordPress. Finalized strategy to overhaul codebase and architecture enabling development of new advanced features.}
        \resumeItem{Infrastructure overhaul $|$ \emph{CI/CD, Monorepo, Puppeteer}}{Implemented a modernized development workflow by implementing standard practices including monorepo, CI/CD, and E2E testing across all products. This reduced code duplication which was a regular source of bugs and improved developer productivity.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Software Engineer (Remote)}{Mar. 2023 -- Feb. 2024}
      {Dotcamp}{Company based in NY, USA}
      \resumeItemListStart
        \resumeItem{\projectWithLinkAndTech{https://github.com/DotCamp/wp-table-builder}{WP Table Builder}{JS, PHP, Vue}}{WP Table Builder is a table builder plugin for WordPress. Worked on adding new backwards compatible features and fixes to legacy codebase. Developed a system to streamline backwards compatibility. Explored strategies to make the legacy codebase modern and efficient.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance}{Jan. 2021 -- Present}
      {Software Engineer}{}
      \resumeItemListStart
        \resumeItem{\projectWithLinkAndTech{https://github.com/permafrost06/diagman}{Diagman}{Vue, Tauri, CF Worker, Turso, Drizzle}}
        {Patient management software for a diagnostic centre. Led development and planning. Deployed using serverless technology.}
        \resumeItem{\projectWithLinkAndTech{https://github.com/permafrost06/dknck}{Sales Software}{Laravel, Vue, MySQL}}
        {Sales software for multiple clothing shops. Led development, planning, and deployment. Deployed in self hosted servers.}
        \resumeItem{Thesis Coding $|$ \emph{Matlab, Arduino, Python, Javascript}}
        {Wrote a simulation program for a master's thesis paper. It analyzes sensor data using Pearson Correlation, Euclidean Distance, NSGA-II, and Monte-Carlo simulation. It is highly optimized and capable of running hundreds of times per second on low end hardware. Assisted in developing a bachelor's thesis and coded multiple ESP32 boards to create a star BLE network and transmit sensor data between them. Created a web portal to display the sensor data and stress test the network.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Shahjalal University of Science and Technology}{Sylhet, Bangladesh}
      {Bachelor of Science in Oceanography}{Feb. 2017 -- Jan. 2021}
  \resumeSubHeadingListEnd


%-----------TEHCNICAL SKILL-----------
\section{Technical Skill}
    \resumeSubHeadingListStart
      \resumeSubItem{Programming languages}
      {TypeScript, JavaScript, PHP, Golang, Python, Bash, Kotlin}
      \resumeSubItem{Frontend Technologies}
      {React, Redux, Tanstack Query, Vue, Nuxt, Pinia, Tailwind, SCSS}
      \resumeSubItem{Backend Technologies}
      {Express, Laravel, Flask, Firebase}
      \resumeSubItem{Database Management}
      {MySQL, SQLite, IndexedDB, PouchDB, Firebase firestore, Drizzle}
      \resumeSubItem{Other Web Technologies}
      {Vite, Webpack, PNPM, PWA, Service Workers, Webhooks, Websockets, Zod}
      \resumeSubItem{Cloud Platforms}
      {AWS, Azure, Linode, Cloudflare, Netlify}
      \resumeSubItem{Version Control}
      {Git, GitHub, Gitlab}
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
